Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-04-13 ms.tex
Figures are temporarily added.

\author{
%
David S. Spiegel\altaffilmark{1, 2} \\
%
{\bf and some order:} \\
%
Jason Nordhaus\altaffilmark{3} \\
%
Nikku Madhusudhan\altaffilmark{4} \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{5} \\
%
Tony Mroczkowski\altaffilmark{6} \\
%
Neil Zimmerman\altaffilmark{7}
}

@@

\section{Introduction}
\label{sec:intro}

@@

\section{Assumpsions}

\subsection{Mechanisms}

\subsection{Properties for Stellar Wind of RGs}

@@

\subsection{Properties for Planetary Magnetic Field}

@@

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. We simply use the same model as \citet{griebmeier2004}, where the density as a function of radius from the center is described as:
%%%%%%%%%% 
\begin{equation}
\rho (r) = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left( \pi \frac{r}{R_p} \right)}{\left( \pi \frac{r}{R_p} \right)} \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
and assume that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$. The density of the metallic core is obtained by averaging the density in the core.

We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

\section{Estimates of Radio Emission from RGHJ}

\subsection{Estimates of frequency}

@@

Since the 
Figure \ref{fig:f_cyclotron} shows

@@

...OK!\memoYF{double-check}

\subsection{Estimates of intensity}

@@

\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Discussion on Observability}

\subsection{Radio emission from red giants stars}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Expected population of RGHJ in the observable volume}

>>>>

\author{
%
Yuka Fujii\altaffilmark{0} \\
%
David S. Spiegel\altaffilmark{1, 2} \\
%
{\bf and some order:} \\
%
Jason Nordhaus\altaffilmark{3} \\
%
Nikku Madhusudhan\altaffilmark{4} \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{5} \\
%
Tony Mroczkowski\altaffilmark{6} \\
%
Neil Zimmerman\altaffilmark{7}
}

\affil{$^0$Earth-Life Science Institute, Tokyo Institute of Technology, 
  Tokyo, JAPAN, 152-8550}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Assumptions}
\label{s:assumptions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mechanisms}
\label{ss:mechanisms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties for Stellar Wind of RGs}
\label{ss:stellarwind}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties for Planetary Magnetic Field}
\label{ss:planetarymagnetic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. We simply use the same model as \citet{griebmeier2004}, where the density as a function of radius from the center is described as:
%%%%%%%%%% 
\begin{equation}
\rho (r) = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left( \pi \frac{r}{R_p} \right)}{\left( \pi \frac{r}{R_p} \right)} \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
where
%%%%%%%%%% 
\begin{equation}
R_p (M_p) = \frac{(\alpha M_p)^{1/3}}{1+\left( \frac{M_p}{M_{\rm max}} \right)} \label{eq:Rp}
\end{equation}
%%%%%%%%%%
with $\alpha =6/1 \times 10^{-4}$ \citep{griebmeier2007}. 
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimates of Radio Emission from RGHJ}
\label{s:estimate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimates of frequency}
\label{ss:frequency}

@@

Figure \ref{fig:f_cyclotron} shows the cyclotron frequency of the planetary magnetic field.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.7\hsize]{test_fcycrotron.eps}
\end{center}
\caption{Cyclotron frequency. (May be deleted eventually.)}
\label{fig:f_cyclotron}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.9\hsize]{test_observability.eps}
\end{center}
\caption{Where condition $f_{cyclotron}>f_{plasma}$. (May be deleted eventually.)}
\label{fig:f_cyclotron}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimates of intensity}
\label{ss:intensity}

@@

Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                                                                                                                               
\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.9\hsize]{test_radio.eps}
\end{center}
\caption{Intensity of radio emission. }
\label{fig:radio}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Will the electron spiraling and offset the magnetic field? (Mehrdad Mirababayi)}
\label{ss:offset}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion on Observability}
\label{s:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio emission from red giants stars}
\label{ss:RGradio}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Expected population of RGHJ in the observable volume}
\label{ss:number}
